Time stability in human interaction networks

### 2015-06-13 paper.tex
pequena correcao enquanto traduzo p quali

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/fser_}
	\caption{Degree distribution of scale-free and Erd\"os-R\'enyi ideal networks.
		The latter has more intermediary vertices, while the former has more peripheral and hub vertices.
		The sector borders are defined by the two intersections $k_L$ and $k_R$ of the connectivity distributions.
		Characteristic degrees are in the compact intervals: $[0,k_L]$, $(k_L,k_R]$, $(k_R,k_{max}]$ for the Erd\"os sectors (periphery, intermediary and hubs).}
		\label{fig:setores}
\end{figure}
i	To ensure statistical validity of the histograms, bins can be chosen to contain at least $\eta$ vertices of the real network. Thus, each bin, starting at degree $k_i$, spans $\Delta_i=[k_{i},k_{j}]$ degree values, where $j$ is the smallest integer with which there are at least $\eta$ vertices with degree larger than or equal $k_i$, and less than or equal $k_{j}$. This changes equation~\ref{criterio} to:

@@

Using equations~\ref{eq:part}, these compound criteria $C_\delta$, with $\delta$ integer in the interval $1<\delta<6$ can be described as:

>>>>

\begin{figure}[!h]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/fser_}
	\caption{Degree distributions of scale-free and Erd\"os-R\'enyi ideal networks.
		The latter has more intermediary vertices, while the former has more peripheral and hub vertices.
		The sector borders are defined by the two intersections $k_L$ and $k_R$ of the connectivity distributions.
		Characteristic degrees are in the compact intervals: $[0,k_L]$, $(k_L,k_R]$, $(k_R,k_{max}]$ for the Erd\"os sectors (periphery, intermediary and hubs).}
		\label{fig:setores}
\end{figure}
To ensure statistical validity of the histograms, bins can be chosen to contain at least $\eta$ vertices of the real network. Thus, each bin, starting at degree $k_i$, spans $\Delta_i=[k_{i},k_{j})$ degree values, where $j$ is the smallest integer with which there are at least $\eta$ vertices with degree larger than or equal $k_i$, and less than $k_{j}$. This changes equation~\ref{criterio} to:

@@

Using equations~\ref{eq:part}, these compound criteria $C_\delta$, with $\delta$ integer in the interval $1\leq\delta<6$ can be described as:
